\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2015-09-26 minimal.tex
changed some filenames
csv as data source Version 1.0.4
corrected line endings
- All PDBF elements use the font size, font family, and font style that was active at the point of their definition. - Lots of Bugfixes

\documentclass[10pt]{article}
\usepackage{PDBF}
\usepackage[a4paper]{geometry}

\dbSQLText{CREATE TABLE test(a int, b int); INSERT INTO test VALUES(1, 10); INSERT INTO test VALUES(2, 100); INSERT INTO test VALUES(3, 120); INSERT INTO test VALUES(4, 100);}
%\dbSQLFile{somedb.sql}
%\dbSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtable}%

\begin{document}
\noindent
\sql{SELECT * FROM test;}\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\[3pt]
The following points are linked to the chart below: \dataText[linkTo=testname, linkSelector=2, linkLabel=Value at 2]{SELECT * FROM test WHERE a=2;}, \dataText[linkTo=testname, linkSelector=3, linkLabel=Value at 3]{SELECT * FROM test WHERE a=3;}.\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=line, name=testname]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=bar]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=signatureplot]{SELECT b FROM test;}\\[3pt]
\multiplotChart[width=\textwidth, height=0.9\textwidth, xCount=2, yCount=2, yValues={["b", "b*2"]}, xValues={["a > 2", "a <= 2"]}, yFirst]{SELECT a,? FROM test WHERE ?;}\\[3pt]
\pivotTable[width=\textwidth, height=0.5\textwidth, rows={["a"]}, aggregationattribute=b]{SELECT * FROM test;}\\[3pt]
\dataTable[verticalLines=i, horizontalLinesHeader=b hh, horizontalLinesBody=i]{SELECT * FROM test;}\\[3pt]
\end{document}

>>>>

\documentclass[10pt]{article}
\usepackage{pdbf}
\usepackage[a4paper]{geometry}

\dbSQLText{CREATE TABLE test(a int, b int); INSERT INTO test VALUES(1, 10); INSERT INTO test VALUES(2, 100); INSERT INTO test VALUES(3, 120); INSERT INTO test VALUES(4, 100);}
%\dbSQLFile{somedb.sql}
%\dbSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtable}%
%\dbCSVFile{result.csv}{test}

\begin{document}
\noindent
\sql{SELECT * FROM test;}\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\[3pt]
The following points are linked to the chart below: \dataText[linkTo=testname, linkSelector=2, linkLabel=Value at 2]{SELECT * FROM test WHERE a=2;}, \dataText[linkTo=testname, linkSelector=3, linkLabel=Value at 3]{SELECT * FROM test WHERE a=3;}.\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=line, name=testname]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=bar]{SELECT * FROM test;}\\[3pt]
\newpage
{\fontfamily{phv} \large \selectfont
\noindent
Change the font before this line to Helvetica and fontsize from 10 to 12.\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=signatureplot]{SELECT b FROM test;}\\[3pt]
\multiplotChart[width=\textwidth, height=0.9\textwidth, xCount=2, yCount=2, yValues={["b", "b*2"]}, xValues={["a <= 2", "a > 2"]}, yFirst]{SELECT a,? FROM test WHERE ?;}\\[3pt]
\pivotTable[width=\textwidth, height=0.5\textwidth, rows={["a"]}, aggregationattribute=b]{SELECT * FROM test;}\\[3pt]
\dataTable[verticalLines=i, horizontalLinesHeader=b hh, horizontalLinesBody=i]{SELECT * FROM test;}\\[3pt]
}
\end{document}

### 2015-09-26 pdbf-doc.tex
corrected line endings
- All PDBF elements use the font size, font family, and font style that was active at the point of their definition. - Lots of Bugfixes

\def\pdbfQuality{4.0}

@@

\subsection{CSV}
\verb|\dbCSVFile[options]{fileWithCSVData}{tableName}| \\[8pt]
\textbf{Note:} Relative filepaths are relative to the tex file.\\[4pt]
\noindent Options:\\[3pt]
%
\option
{headers}
{Defines the names of columns for the CSV file. If not set the first line of the CSV file is used as header.}
{Javascript-Array of Strings}
{\texttt{[]}}

@@

\section{PDBF elements}
\subsection{Chart}
\begin{figure}[h!]%
\hspace{-218pt}Examples:\\
    \centering
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=line]{SELECT * FROM test;}
    \caption{Line Chart}
    \end{minipage}
    \hspace{11pt}
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=bar]{SELECT * FROM test;}
    \caption{Bar Chart}
    \end{minipage} \\[8pt]

    \begin{minipage}{1.0\textwidth}
    \chart[width=\textwidth, height=0.36\textwidth, chartType=signatureplot]{SELECT b FROM test;}
    \caption{Signatureplot Chart}
    \end{minipage}
%    \begin{minipage}{.48\textwidth}
%    \chart[width=\textwidth, height=0.8\textwidth, chartType=signatureplot]{SELECT * FROM test;}
%    \caption{Signatureplot Chart}
%    \end{minipage}
%    \hspace{11pt}
%    \begin{minipage}{.48\textwidth}
%    \chart[width=\textwidth, height=0.8\textwidth, chartType=Line, xunit=Date, yunit={Runtime [in sec]}, options={"strokeWidth": 0, "drawPoints": true, "pointSize": 3, "highlightCircleSize": 4, "xRangePad": 10}]{SELECT date, runtimeA AS [engine A], runtimeB AS [engine B] FROM data2;}
%    \caption{Multi-column Dot Chart}
%    \end{minipage}
\end{figure}

@@

\option
{quality}
{Sets the quality for the image version of the chart in the pdf. 1.0 corresponds roughly to 120 pixels per inch. Can also be redefined globally (\texttt{pdbfQuality}).}
{Number $>$ 0}
{\texttt{1.0}}

\option
{scale}
{Scales the size of the chart. 1.0 corresponds roughly to font-size that is currently choosen in \LaTeX. Can also be redefined globally (\texttt{pdbfScale}).}
{Number $>$ 0}
{\texttt{1.0}}

@@

%\option %TODO: not yet implemented
%{logscale}
%{If set, the y axis uses log scale. Can also be redefined globally (\texttt{pdbfLogscale}).}
%{\texttt{true} or \texttt{false}}
%{\texttt{false}}
%
%\option %TODO: not yet implemented
%{overlap}
%{Unused.}
%{\texttt{TODO: ...}}
%{\texttt{TODO: ...}}
%
%\option %TODO: not yet implemented
%{legendpos}
%{Sets the position of the legend of the chart.}
%{\texttt{TODO: ...}}
%{\texttt{TODO: ...}}
%

@@

\noindent Macros: \\[3pt]
\verb|\pivotTable[options][queryForOverlay]{queryForPage}| \\
\textbf{Note:} if \verb|queryForOverlay| is omitted the \verb|queryForPage| is used for the overlay\\[8pt]
\noindent Options: \\[3pt]
%
\option
{width}
{Sets the width of the chart.}
{\LaTeX~length}
{No default value. Value must always be set!}

\option
{quality}
{Sets the quality for the image version of the chart in the pdf. 1.0 corresponds roughly to 120 pixels per inch. Can also be redefined globally (\texttt{pdbfQuality}).}
{Number $>$ 0}
{\texttt{1.0}}

\option
{scale}
{Scales the size of the chart. 1.0 corresponds roughly to font-size that is currently choosen in \LaTeX. Can also be redefined globally (\texttt{pdbfScale}).}
{Number $>$ 0}
{\texttt{1.0}}

@@

\option
{cols}
{The attributes for the columns in the pivot table.}
{JavaScript array of strings (e.g. ["a", "b", "c"]). The name of attributes have to be present in the result of the sql query for the overlay and page}
{\texttt{[]} (which means empty array)}

@@

\subsection{DataText}
Write text that is the result of a SQL-statement.\\[3pt]
Example:\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\
The table ``test'' contains the following tuples: \dataText{SELECT * FROM test;}.\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\dataText[options]{query}| \\[8pt]

>>>>

\def\pdbfQuality{2.0}

@@

\subsection{CSV}
\textbf{Note:} By default the first line of the CSV file is used as attribute names for the table. You can use the header option to manually specify attribute names.\\[3pt]
\verb|\dbCSVFile[options]{fileWithCSVData}{tableName}| \\[8pt]
\textbf{Note:} Relative filepaths are relative to the tex file.\\[4pt]
\noindent Options:\\[3pt]
%
\option
{headers}
{Defines the names of columns for the CSV file. If not set the first line of the CSV file is used as header.}
{Javascript-Array of Strings}
{\texttt{[]}}

@@

\section{PDBF elements}
\textbf{Note:} All PDBF elements use the font size, font family, and font style that was active at the point of their definition. You can for example surround all commands with \verb|\textbf{...}|, \verb|\emph{...}| or any other font command.\\[3pt]
\subsection{Chart}
\begin{figure}[h!]%
\hspace{-218pt}Examples:\\
    \centering
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=line]{SELECT * FROM test;}
    \caption{Line Chart}
    \end{minipage}
    \hspace{11pt}
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=bar]{SELECT * FROM test;}
    \caption{Bar Chart}
    \end{minipage} \\[8pt]
    \begin{minipage}{1.0\textwidth}
    \chart[width=\textwidth, height=0.36\textwidth, chartType=signatureplot]{SELECT b FROM test;}
    \caption{Signatureplot Chart}
    \end{minipage}
\end{figure}

@@

\option
{quality}
{Sets the quality for the image version of the chart in the pdf. 1.0 corresponds roughly to 240 pixels per inch. Can also be redefined globally (\texttt{pdbfQuality}).}
{Number $>$ 0}
{\texttt{1.0}}

@@

\option
{logscale}
{If set, the y-axis uses log scale. Can also be redefined globally (\texttt{pdbfLogscale}).}
{\texttt{true} or \texttt{false}}
{\texttt{false}}

%\option %TODO: not yet implemented
%{overlap}
%{Unused.}
%{\texttt{TODO: ...}}
%{\texttt{TODO: ...}}
%
%\option %TODO: not yet implemented
%{legendpos}
%{Sets the position of the legend of the chart.}
%{\texttt{TODO: ...}}
%{\texttt{TODO: ...}}
%

@@

\noindent Macros: \\[3pt]
\verb|\pivotTable[options][queryForOverlay]{queryForPage}| \\
\textbf{Note:} if \verb|queryForOverlay| is omitted the \verb|queryForPage| is used for the overlay\\[8pt]
\noindent Options: \\[3pt]
%
\option
{width}
{Sets the width of the table.}
{\LaTeX~length}
{No default value. Value must always be set!}

\option
{height}
{Sets the height of the table.}
{\LaTeX~length}
{No default value. Value must always be set!}

\option
{quality}
{Sets the quality for the image version of the table in the pdf. 1.0 corresponds roughly to 240 pixels per inch. Can also be redefined globally (\texttt{pdbfQuality}).}
{Number $>$ 0}
{\texttt{1.0}}

@@

\option
{cols}
{The attributes for the columns in the pivot table. \textbf{Note:} This feature is currently broken!}
{JavaScript array of strings (e.g. ["a", "b", "c"]). The name of attributes have to be present in the result of the sql query for the overlay and page}
{\texttt{[]} (which means empty array)}

@@

\subsection{DataText}
Write text that is the result of a SQL-statement.\\
\textbf{Note:} DataText can be linked to other PDBF elements (Currently only charts supported). This means that if you move the mouse over this DataText then the specified data in the linked PDBF element is highlighted.\\[3pt]
Example:\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\
The table ``test'' contains the following tuples: \dataText{SELECT * FROM test;}.\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\dataText[options]{query}| \\[8pt]
